GMU MS SWE Handbook\\{\large A Handbook For the Masters of Software Engineering program at George Mason University

### 2025-02-23 phd-cs-us/demystify.tex
updates

    {\fontsize{16}{19.2} \selectfont \textcolor{ForestGreen}{\bf ThanhVu (Vu) Nguyen}}\\[0.1in]
    George Mason University, Dept. of Computer Science\\[0.1in]
    \today{} (latest version available on  \href{https://github.com/nguyenthanhvuh/phd-cs-us}{Github})
    };
    \end{tikzpicture}

@@

\begin{center}
  \href{https://nguyenthanhvuh.github.io/phd-cs-us/demystify.pdf}{nguyenthanhvuh.github.io/phd-cs-us/demystify.pdf},
\end{center}

\noindent and its \LaTeX{} source is also on \href{https://github.com/nguyenthanhvuh/phd-cs-us}{GitHub}. If you have questions or comments, feel free to create new \href{https://github.com/nguyenthanhvuh/phd-cs-us/issues}{GitHub issues} or \href{https://github.com/nguyenthanhvuh/phd-cs-us/discussions}{discussions}.

>>>>

    {\fontsize{16}{19.2} \selectfont \textcolor{ForestGreen}{\bf ThanhVu (Vu) Nguyen}}\\[0.1in]
    George Mason University, Dept. of Computer Science\\[0.1in]
    \today{} (latest version available on  \href{https://github.com/dynaroars/books/phd-cs-us}{Github})
    };
    \end{tikzpicture}

@@

\begin{center}
  \href{https://dynaroars.github.io/books/phd-cs-us/demystify.pdf}{dynaroars.github.io/books/phd-cs-us/demystify.pdf},
\end{center}

\noindent and its \LaTeX{} source is also on \href{https://github.com/dynaroars/books/phd-cs-us}{GitHub}. If you have questions or comments, feel free to create new \href{https://github.com/dynaroars/books/issues}{GitHub issues} or \href{https://github.com/dynaroars/books/discussions}{discussions}.
